### 2022-02-06 ms_body/manuscript.Rmd
Add LaTex manuscript document and template

---
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: ../svm-latex-ms.tex
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{hyperref}
- \setlength\parindent{24pt}
- \usepackage{multirow}
- \usepackage{helvet}
- \usepackage{setspace}
- \renewcommand\familydefault{\sfdefault}
biblio-style: apsr
geometry: margin=1in
fontfamily: mathpazo
bibliography: refs.bib
csl: biological-control.csl
fontsize: 12pt
spacing: double
indent: yes
endnote: no
include-before: '`\newpage{}`{=latex}'
---

@@

```{r import_fig_1, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_1.png"), dpi = NA)
```

@@

```{r import_fig_2, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_2.png"), dpi = NA)
```

@@

```{r import_fig_3, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_3.png"), dpi = NA)
```

@@

```{r import_fig_4, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_4.png"), dpi = NA)
```

@@

```{r import_fig_5, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_5.png"), dpi = NA)
```

@@

```{r import_fig_6, echo = FALSE}
knitr::include_graphics(here::here("./ms_body/ms_figs/fig_6.png"), dpi = NA)
```

>>>>

---
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: "./_ms_template/svm-latex-ms.tex"
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{hyperref}
- \setlength\parindent{24pt}
- \usepackage{multirow}
- \usepackage{helvet}
- \usepackage{setspace}
- \renewcommand\familydefault{\sfdefault}
biblio-style: apsr
geometry: margin=1in
fontfamily: mathpazo
bibliography: "./ref_list/refs.bib"
csl: "./ref_list/biological-control.csl"
fontsize: 12pt
spacing: double
indent: yes
endnote: no
include-before: '`\newpage{}`{=latex}'
---

@@

```{r import_fig_1, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_1.png"), dpi = NA)
```

@@

```{r import_fig_2, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_2.png"), dpi = NA)
```

@@

```{r import_fig_3, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_3.png"), dpi = NA)
```

@@

```{r import_fig_4, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_4.png"), dpi = NA)
```

@@

```{r import_fig_5, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_5.png"), dpi = NA)
```

@@

```{r import_fig_6, echo = FALSE}
# knitr::include_graphics(here::here("./ms_body/ms_figs/fig_6.png"), dpi = NA)
```
